---
title: "ggplot2 nba themes, scales, and geoms"
output:
  html_document:
    fig_height: 5
    fig_width: 8
    keep_md: yes
---

This package contains ggplot2 themes, scales, and geoms, for all 30 NBA teams. All of the code included in this package was taken directly from Ricardo Bion's [ggtech package](https://github.com/ricardo-bion/ggtech/) and modified for use with NBA team colors and logos. 

### Install ggnba:

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r, install, eval = FALSE}

devtools::install_github("spirgel/ggnba", 
                          dependencies=TRUE)

```

### Use ggnba

```{r, base_graph}

library(ggnba)
library(tidyverse)

d <- diamonds %>% 
  filter(color == "G" | color == "H" |
           color == "I" | color == "J") %>% 
  ggplot(aes(x = carat, fill = color)) +
  geom_histogram(color = "black")
  
```

```{r, heat_theme}

d + theme_nba("heat") +
  scale_fill_nba("heat") +
  labs(title = "Miami Heat theme")

```

```{r, grizzlies_theme}

d + theme_nba("grizzlies") +
  scale_fill_nba("grizzlies") +
  labs(title = "Memphis Grizzlies theme")


```

```{r, kings_theme}

d + theme_nba("kings") +
  scale_fill_nba("kings") +
  labs(title = "Sacramento Kings theme")

```

As mentioned, the code for this package was modified from Ricardo Bion's ggtech package. His `geom_tech` was inspired by [emoGG](https://github.com/dill/emoGG), thus, so is `geom_nba`.

```{r, geom_data}

d2 <- data.frame(x = c(1:4, 3:1), y=1:7)

```

```{r, heat_geom}

ggplot(d2, aes(x = x, y = y)) + 
  geom_nba(size=0.25, theme = "heat") + 
  theme_nba("heat") +
  ggtitle("Miami Heat geom")

```

```{r, grizzlies_geom}

ggplot(d2, aes(x = x, y = y)) + 
  geom_nba(size=0.25, theme = "grizzlies") + 
  theme_nba("grizzlies") +
  ggtitle("Memphis Grizzlies geom")

```

```{r, kings_geom}

ggplot(d2, aes(x = x, y = y)) + 
  geom_nba(size=0.25, theme = "kings") + 
  theme_nba("kings") +
  ggtitle("Sacramento Kings geom")

```
